{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Predictions for BHBH, BHNS and NSNS binaries in LISA

### 2021-07-29 paper/tex/sections/variations.tex
change all figure names to organise
add quick links to plots

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{3_dco_detections.pdf}
    \caption{The number of expected detections in the LISA mission for different DCO types and model variations. Error bars show the 1- (solid) and 2-$\sigma$ (dotted) Poisson uncertainties. An arrow indicates that the error bar extends to zero. The left axis and grid lines show the number of detections in a 4-year LISA mission and the right axis shows an approximation of the number of detections in a 10-year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates). Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{app:fiducial_physics}. See Sec.~\ref{sec:detection_rate_analysis} for a discussion. \todo{Will add H, I, J, R, T once Floor says that they are done}}
    \label{fig:detection_rates}
\end{figure*}

@@

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{lower_mass_gap_rapid_variation.pdf}
    \caption{Comparison of the component mass distribution of LISA detectable DCOs when using the Fryer delayed (model \modFid{}) and rapid (model \modRapid{}) remnant mass prescriptions. Distributions are plotted in the same way as Fig.~\ref{fig:fiducial_pdf_distributions}}
    \label{fig:lower_mass_gap_variation}
\end{figure}

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{ecc_low_kick_variation.pdf}
    \caption{As lower left panel of Fig.~\ref{fig:fiducial_pdf_distributions}, but for model \modSigLower{}. For comparison, we show the mean distribution for the fiducial model as dashed lines.}
    \label{fig:ecc_low_kick_variation}
\end{figure}

>>>>

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{fig7_dco_detections.pdf}
    \caption{The number of expected detections in the LISA mission for different DCO types and model variations. Error bars show the 1- (solid) and 2-$\sigma$ (dotted) Poisson uncertainties. An arrow indicates that the error bar extends to zero. The left axis and grid lines show the number of detections in a 4-year LISA mission and the right axis shows an approximation of the number of detections in a 10-year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates). Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{app:fiducial_physics}. See Sec.~\ref{sec:detection_rate_analysis} for a discussion. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig7_dco_detections.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}. \todo{Will add R, T once Floor says that they are done}}
    \label{fig:detection_rates}
\end{figure*}

@@

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{fig8_lower_mass_gap_rapid_variation.pdf}
    \caption{Comparison of the component mass distribution of LISA detectable DCOs when using the Fryer delayed (model \modFid{}) and rapid (model \modRapid{}) remnant mass prescriptions. Distributions are plotted in the same way as Fig.~\ref{fig:fiducial_pdf_distributions}. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig8_lower_mass_gap_rapid_variation.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
    \label{fig:lower_mass_gap_variation}
\end{figure}

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{fig9_ecc_low_kick_variation.pdf}
    \caption{As lower left panel of Fig.~\ref{fig:fiducial_pdf_distributions}, but for model \modSigLower{}. For comparison, we show the mean distribution for the fiducial model as dashed lines. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig9_ecc_low_kick_variation.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
    \label{fig:ecc_low_kick_variation}
\end{figure}
